A load balancing scheme for massively multiplayer online games

### 2009-04-29 textos/dissertation/MTAP_LaTeX/pub/tex/latex/svjour3/global/balancing.tex

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2006/03/15
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallextended]{svjour3}     % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}         % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage{algorithmic}
\usepackage{algorithm}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}
%[TODO:ajustar TODAS as \refs]
\title{A load balancing scheme for massively multiplayer online games %\thanks{}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{figure}
%% Use the relevant command to insert your figure file.
%% For example, with the graphicx package use
	\includegraphics[width=0.2\linewidth]{images/Fig-Bezerra.jpg}

	\textbf{Carlos Eduardo Benevides Bezerra} is a full-time Ph.D. student at UFRGS (Universidade Federal do Rio Grande do Sul). He obtained his M.Sc. from the same university in 2009 and his B.Sc. degree from UFBA (Universidade Federal da Bahia) in 2007.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

\begin{figure}
%% Use the relevant command to insert your figure file.
%% For example, with the graphicx package use
  \includegraphics[width=0.2\linewidth]{images/Fig-Geyer.jpg}

  \textbf{Cláudio Fernando Resin Geyer} is a full-time Professor at UFRGS.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2006/03/15
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallextended]{svjour3}     % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}         % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{times}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}
%[TODO:ajustar TODAS as \refs]
\title{A load balancing scheme for massively multiplayer online games %\thanks{}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{figure}[h]
%% Use the relevant command to insert your figure file.
%% For example, with the graphicx package use
	\includegraphics[width=0.3\linewidth]{images/Fig-Bezerra.jpg}

	\textbf{Carlos Eduardo Benevides Bezerra} is a full-time Ph.D. student at UFRGS (Universidade Federal do Rio Grande do Sul). He obtained his M.Sc. from the same university in 2009 and his B.Sc. degree from UFBA (Universidade Federal da Bahia) in 2007. His research interests include massively multiplayer online games, interest management algorithms, parallel and distributed algorithms, peer-to-peer networks and computational geometry.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

\begin{figure}[h]
%% Use the relevant command to insert your figure file.
%% For example, with the graphicx package use
  \includegraphics[width=0.3\linewidth]{images/Fig-Geyer.jpg}

  \textbf{Cláudio Fernando Resin Geyer} is an associate professor at the Informatics Institute of the Federal University of Rio Grande do Sul. His research interests include massively multiplayer games, grid computing and ubiquitous computing. He received his Ph.D. in informatics from Joseph Fourier University. He is a member of ACM and of the Brazilian Computer Society (SBC).

%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:geyer}       % Give a unique label
\end{figure}
